Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 results.tex
next round of comments
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@978 ccdd05d5-56c1-461a-bf98-85f6876523b4

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim 10^8$
\flops\ to cover a sub-bank comprising $\sim 10^2$ out of the total $\sim
10^5$ mass pairs.  Given that modern (ca. 2011) workstations can sustain
computation rates up to $\sim 10^{10}$ \flops{}, and assuming that other
regions of the parameter space have similar computational scaling\footnote{The
lengths of templates varies over the parameter space; lower-mass templates are
longer and would require more computation to analyze while higher-mass
templates are shorter and would require less. However, we consider the
estimates based on this sub-bank to be a reasonable representation.}, an entire
search could be implemented with $\gtrsim 10$ machines.

By comparison, using the \TD\ method to achieve the same latency costs $\sim 10^{13}$ \flops\ for this particular sub-bank, and so it would require $\sim 10^6$ present-day machines.  Presently, the \LIGO{} Data Grid consists of only $\sim 10^4$ machines.

>>>>

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim 10^8$
\flops\ to cover a sub-bank comprising $\sim 10^2$ out of the total $\sim 10^5$
mass pairs.  Given that modern (ca. 2011) workstations can sustain computation
rates up to $\sim 10^{10}$ \flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire search could be
implemented with $\gtrsim 10$ machines.  The lengths of templates does vary
over the parameter space; lower-mass templates are longer and would require
more computation to analyze while higher-mass templates are shorter and would
require less. However, we consider the estimates based on this sub-bank to be a
reasonable representation.

By comparison, using the \TD\ method to achieve the same latency costs $\sim
10^{13}$ \flops\ for this particular sub-bank, and so it would require $\sim
10^6$ present-day machines to search the full parameter space.  Presently, the
\LIGO{} Data Grid consists of only $\sim 10^4$ machines.
